%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Santiago Donadio} \\ \vspace{5pt}
    \small \href{sms:3392419039}{\underline{339-241-9039}} $|$ \href{mailto:santiagohdonadio@icloud.com}{\underline{santiagohdonadio@icloud.com}} $|$
    \href{https://www.linkedin.com/in/santiagodonadio/}{\underline{LinkedIn}} $|$
    \href{https://github.com/santiagodonadio/}{\underline{GitHub}} % $|$ \textbf{U.S. Citizen}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\vspace{7pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Worcester State University}{Worcester, MA}
      {Bachelor of Science in Computer Science, Concentration in Software Development}{August 2022 — May 2026}
      
      \resumeItemListStart
        \resumeItem{Upsilon Pi Epsilon Member - International Honor Society for the Computing and Information Disciplines}
        \resumeItem{\href{https://programmingwithsantiago.wordpress.com}{\underline{Programming with Santiago}} - A personal blog covering a wide range of programming topics.}
        
      \resumeItemListEnd
    
 % \resumeSubHeadingListEnd
%\vspace{5pt}
 % \resumeSubHeadingListStart
  %  \resumeSubheading
   %   {Quinsigamond Community College}{Worcester, MA}
    %  {Associates Degree in Liberal Arts (GPA: 4.0)}{Jan. 2021 -- Aug. 2022}
    
  \resumeSubHeadingListEnd


\vspace{0pt}


%-----------PROJECTS-----------
\section{Experience}
\vspace{7pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\href{https://apps.apple.com/us/app/boardai/id6759064114}{\underline{\textbf{Independent: Board AI}}} $|$ \emph{Swift, JavaScript, Firebase, OpenAI, Cloud Scheduler}}{November 2025 — Present}
          \resumeItemListStart
            \resumeItem{Built and launched \textbf{Board AI} on the Apple App Store to provide users with personalized, AI generated daily content.}
            \resumeItem{Integrated \textbf{Large Language Models (LLMs)} via API to architect a dynamic board generation system enabling custom, user prompted content delivery.}
            \resumeItem{Architected a scalable backend using \textbf{Firebase (Firestore \& Authentication)} and \textbf{JavaScript (Cloud Functions)} to manage user profiles, synchronized content feeds, and real time data persistence.}
          \resumeItemListEnd
          \vspace{5pt}



      \resumeProjectHeading
        {\textbf{University: Thea's Pantry: IAM Team} $|$ \emph{JavaScript, Keycloak, Express.js}}{Spring Semester 2026}
        \resumeItemListStart
        \resumeItem{Engineering a centralized authentication system using \textbf{Keycloak}.}
        \resumeItem{Implemented \textbf{Role-Based Access Control (RBAC)} to secure sensitive pantry data across multiple services.}
        \resumeItem{Collaborated in a \textbf{Scrum} team of four, utilizing \textbf{GitLab} for version control.}
        \resumeItemListEnd
        \vspace{5pt}

       \resumeProjectHeading
      {\href{https://1drv.ms/w/c/5a6247e5ff8fe0f6/ER1vxZVDSTdDuwq7e64LiC0BxLbVG-bMmuwAkIRkvRwFTg?e=sDPXdG}{\underline{\textbf{University: Predictive Modeling and Data Mining Project}}} $|$  \emph{Kaggle, R, RStudio, WEKA}}{Fall Semester 2025}
          \resumeItemListStart
            \resumeItem{Preprocessed a Kaggle job satisfaction dataset using \textbf{R}, cleaning and transforming 500 records to enable accurate predictive modeling inputs.}
            \resumeItem{Developed \textbf{statistical models} and \textbf{data visualizations} in \textbf{R} and \textbf{WEKA} to identify key correlations between professional environment and employee happiness.}
            \resumeItem{Applied \textbf{Exploratory Data Analysis (EDA)} and data mining techniques to extract actionable insights and validate predictive accuracy for job satisfaction factors.}
          \resumeItemListEnd
          \vspace{5pt}

      \resumeProjectHeading
      {\href{https://facingyoshinobuyamamoto.vercel.app/}{\underline{\textbf{Independent: Pitching Simulator with Yoshinobu Yamamoto}}} $|$ \emph{HTML, CSS, JavaScript}}{November 2025}
      \resumeItemListStart
        \resumeItem{Developed an interactive \textbf{React-based simulator} that utilizes \textbf{MLB Statcast data} to model pitch outcomes against Yoshinobu Yamamoto's specific six pitch repertoire.}
        \resumeItem{Engineered a \textbf{probabilistic algorithm} to calculate batting results by mapping user inputs against real-world \textbf{pitch distributions} and location.}
        \resumeItem{Designed a responsive UI/UX using \textbf{HTML, CSS, and JavaScript} to visualize complex pitch sequencing, allowing users to experience the statistical difficulty of securing a hit against Yamamoto.}
      \resumeItemListEnd
      

    %   \resumeProjectHeading
    %   {\href{https://martian-ascii-project.vercel.app}{\underline{\textbf{Project: Hexadecimal ASCII Translation}}} $|$ \emph{HTML, CSS, JavaScript, React}}{October 2025}
    %       \resumeItemListStart
    %         \resumeItem{Developed a React based tool to convert user input into hexadecimal ASCII that has the potential to be used by anyone.}
    %         \resumeItem{Inspiration: A scene came on in \emph{The Martian} where Matt Damon's character utilized an ASCII table to translate NASA's message. As a Computer Science major, I thought this was very cool and wanted to try coding a Hex ASCII Translator.}
    %       \resumeItemListEnd
    %       \vspace{5pt}

    
    \resumeSubHeadingListEnd

\vspace{1pt}    
%

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\vspace{7pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Java, Python, JavaScript, Swift, C, Ada, SQL, R} \\[6pt]
    \textbf{Frameworks \& Libraries}{: SwiftUI, React, Vue.js, Node.js, Express.js, OpenAI API} \\[6pt]
    \textbf{Cloud \& Backend}{: Firebase (Firestore, Auth, Functions), Keycloak (IAM), Google Cloud Platform} \\[6pt]
    \textbf{Tools \& Platforms}{: GitLab, GitHub, Docker, Xcode, RStudio, WEKA}
  }}
\end{itemize}


\end{document}
